\section{Scrum}
Scrum is an iterative and incremental development framework that coincides with the agile philosophy. Scrum handles requirements a little different than many other more traditional project models. Whereas many project models write requirements with "The system shall"-statements, Scrum uses User Stories placed in the Prouct Backlog. This is the backbone of all Scrum projects and it is our equivalent to a requirements document. A short introduction to some important elements in Scrum will follow. 


\subsection{Backlog}
Scrum has two types of backlogs, the Product Backlog and the Sprint Backlog.
\\ \\ 
\textbf{The Product Backlog} is a prioritized list of customer-centric features. It breaks the project, and every thing you wish to do, down into manageable increments of work called Product Backlog Items(PBIs). These are what we call "User Stories". Product backlog items are not tasks, but they can be broken down into smaller pieces or tasks. Items toward the top of the Product Backlog should be small enough so that a team could accomplish several of them (including proper testing, integration, etc.) in two-week Sprint. The Product Backlog are prioritized from highest- to lowest priority where the topmost item is the one with the highest priority.   
\\ \\ 
\textbf{The Sprint Backlog} is a collection of the user stories which the team plan to accomplish during the Sprint. This is normally created at the Sprint Planning meeting where team members can pick user stories from the Product Backlog and drag it into the Sprint Backlog. The team decide for themselves what they are able to do in the next Sprint. After the team has selected User Stories, they are broken down to smaller tasks. These tasks are sorted as "to do", "in progress", "done" and "approved". As a general rule, one task should never exeed 3 days of work and should ideally be less than one days work. If they are bigger than this, they should be broken down further to smaller more manageable tasks. If the Product Backlog Items are time-estimated, they are estimated in relative units such as story points and estimated relative to each other.
\\ \\ 
To summarize: The Product Backlog concerns everything the team might ever do, or the "requirements", and the Sprint Backlog concern the User Stories which is intended to be accomplished during the next Sprint.  
  
%%%%%%%%


\subsection{User Stories}
The Product Backlog Items (PBIs) are often referred to as User Stories. These are features or "requirements" derived from what the customer wants. These are often written from the perspective of the end user and with the customer in mind. The syntax is \textit{As a/an(user), I want/need, So that(purpose)}. The purpose of writing User Stories is to understand what the customer want. Therefor, these Stories are often derived from conversations with the customer or stakeholders. Whereas other project models use a more standard way of representing requirements i.e the IEEE-830 Standard with \textit{"The system shall.."} - statements, Scrum use User Stories. The \textit{The system shall..}-statements often get hard to prioritize in a agile and incremental project. This is where Scrum has an advantage.
\\ \\
\textbf{Example of a User Story} \\
As a customer, I want the quadrotor to weigh less than 2.5kg. So that laws and regulations are held 

\subsection{Acceptance Criteria}
In Scrum each user story has an Acceptance Criterion. It provides the requirement that have to be met for a user story to be assessed as complete.  
The syntax of these are: \textit{Given(some context), When(some action is carried out), Then(something expected).} \\
\\ 
\textbf{An example of an Acceptance Criterion} \\
Given that we have a quadrotor, When the quadrotor is weighed Then it shall be less than 2.5kg.



