\section{User Story Cards}

\st{ }
% BL001
%\krav{BL001}{N002}{VPQ-16}{}{}{}{As an Engineer, I want a controller so that I can ensure stability for the quadrotor} 

% BL002
%\krav{BL002}{N012}{VPQ-11}{}{}{}{As a customer, I want easily modifiable design so that I can perform quick modifications}

% BL003
\krav{BL003}{N010}{VPQ-13}{}{}{}{As a customer, I want the system to weigh less than 2.5kg so that laws and regulations are held}

% BL004
%\krav{BL004}{N004, N019}{VPQ-22}{}{}{}{\shortstack[l]{As an engineer, I want the quadrotor to do basic flight maneuvers so that we can test simple \\ flight dynamics}}

% BL005
%\krav{BL005}{N015}{VPQ-14}{}{}{}{As an engineer, I want a onboard chip so that I can communicate with the external computer} 

% BL006 
%\krav{BL006}{N014, N015}{VPQ-15}{}{}{}{\shortstack[l]{As an engineer, I want a system that communicate with Qualisys so that we can use the \\ tracking system available}} 

% BL007
%\krav{BL007}{N013, N008, N009}{VPQ-23}{}{}{}{As an engineer, i want materials so that we can build the quadrotors}

% BL008
\krav{BL008}{N003}{VPQ-20}{}{}{}{As a tester, I want to plan the route for the quadrotor so that I can reproduce test results}

% BL009
%\krav{BL009}{N003, N005, N008, N009, N004}{VPQ-18}{}{}{}{\shortstack[l]{As an engineer, I want a mathematical model of flight dynamics so that we can design a \\stable controller}}

% BL010
%\krav{BL010}{N006}{VPQ-17}{}{}{}{\shortstack[l]{As a customer, I want the quadrotors to be as similar as possible so that the comparison \\ is as exact as possible}}

% BL011
\krav{BL011}{N003, N019}{VPQ-12}{AC004, AC005, AC006}{}{1}{As a software developer, I want a simulation of the quadrotor so that we can simulate flight dynamics}

% BL012
%\krav{BL012}{N008, N009, N013}{VPQ-21}{AC007, AC008}{}{1}{As an engineer, I need components so that we can build a quadrotor}

% BL013
%\krav{BL013}{N002, N014}{VPQ-29}{AC001, AC002, AC003}{}{1}{As an engineer, I want an arduino car so that I can test communication in Qualisys}

% BL014
%\krav{BL014}{N021}{VPQ-59}{AC010}{TXXX}{X}{As an engineer, I need atleast four markers so that Qualisys is able to identify position in 6DOF}

% BL015
%\krav{BL015}{N007}{VPQ-60}{}{}{}{As an engineer, I want to test power consumption so that we get information about efficency}

% BL016
%\krav{BL016}{N002, N011, N014}{VPQ-61}{}{}{}{As a customer, I want the quadrotor to be smaller than 400mm so that it will fit in KIC test facility}

% BL017
%\krav{BL017}{N008, N009, N020}{VPQ-62}{}{}{}{\shortstack[l]{As a customer, I want the quadcopters to have a X-shaped frame \\ so that the quadrotor does not favor any flight direction}}

% BL018
%\krav{BL018}{N007, N016, N017}{VPQ-63}{}{}{}{As a customer, I want the quadrotor to have sufficient battery so that we are able to test}

% BL019
\krav{BL019}{N001}{VPQ-19}{}{}{1}{As a student, I need to document our work so that we are able to be evaluated}

% BL020
\krav{BL020}{N018}{VPQ-64}{}{}{}{As a customer, I want a safety mechanism so that we are able to prevent accidents}

% BL021
%\krav{BL021}{N015}{VPQ-66}{}{}{}{As a customer, I want an onboard chip so that I can send control signals to the motors  and servos}

% BL022
\krav{BL022}{N005}{VPQ-67}{}{}{}{As a customer, I want to know how Variable Pitch affects response time}

% BL023
\krav{BL023}{N017}{VPQ-68}{}{}{}{As an Engineer, I need to design the electrical layout so that I can design the quadrotor.}

% BL024 
\krav{BL024}{N001}{VPQ-74}{}{}{2}{As students, we need to publish a webpage so that we can meet the schools demands.}

% BL025
\krav{BL025}{N/a}{VPQ-77}{}{}{2}{As an engineer, I need to do electrical construction so that I can build the quadrotors.}

% BL026
\krav{BL026}{N/a}{VPQ-79}{}{}{2}{As an engineer, I need to create a prototype so that we can perform tests.}

% BL027
\krav{BL027}{N/a}{VPQ-80}{}{}{2}{As an engineer, I need to make a preliminary control system so that we can design the control system.}

% BL028
\krav{BL028}{N/a}{VPQ-101}{}{}{2}{As an engineer, I need a Variable Pitch mechanism so that I can design a working VPQ.}

% BL029
\krav{BL029}{N/a}{VPQ-133}{}{}{2}{\shortstack[l]{As an engineer, I need to est if I can make on propeller stable \\so that we can gather information about how hard it will be to make a flight controller}}

% BL030
\krav{BL030}{N/a}{VPQ-73}{}{}{3}{As an engineer I need to create the foundation of the flight controller so that we can test the quadrotors.}

% BL031
\krav{BL031}{N/a}{VPQ-83}{}{}{}{As an engineer, I need a mathematical model for FPQ so that we can design the control system.}

% BL032
\krav{BL032}{N/a}{VPQ-106}{}{}{4}{\shortstack[l]{As an engineer, I need a basic flight controller so that I can test the quadrotor and \\ gain valuable information.}}

% BL033
\krav{BL033}{N/a}{VPQ-107}{}{}{3,4}{\shortstack[l]{As an engineer, I need a basic controller so that we can test the prototype and gain valuable \\ information.}}

% BL034
\krav{BL034}{N/a}{VPQ-113}{}{}{4}{As an engineer, I need a preliminary construction so that I can build the VPQ.}

% BL035
\krav{BL035}{N/a}{VPQ-178}{}{}{4}{As an engineer, I need to construct a FPQ s that I can test motors and thurst.}

% BL036
\krav{BL036}{N/a}{VPQ-184}{}{}{4}{As an engineer, I need to build a FPQ testrig so that I caan test motors and thrust.}

% BL037
\krav{BL037}{N/a}{VPQ-184}{}{}{4}{As an engineer, I need to build a Variable Pitch mechanism testrig.} 

% BL038
\krav{BL038}{N/a}{VPQ-102}{}{}{4}{As students we need to plan the research paper so that we can satisfy the demand of the school.}

% BL039
\krav{BL039}{N/a}{VPQ-110}{}{}{4}{As an engineer, I need a mathematical model for VPQ so that I can design the control system.} 

% BL040
\krav{BL040}{N/a}{VPQ-104}{}{}{}{As an engineer, I need to plan the mechanical design of VPQ so that we are able to build it.}

% BL041
\krav{BL041}{N/a}{VPQ-120}{}{}{}{As an engineer I need to control the servos with Arduino so that we can control pitch.}

% BL042
\krav{BL042}{N001}{VPQ-24}{}{}{}{As students we need to document our work so that we can be evaluated(second presentation).}

% BL043
\krav{BL043}{N001}{VPQ-25}{}{}{}{As students we need to document our work so that we can be evaluated(final presentation).}

% BL044
\krav{BL044}{N001}{VPQ-70}{}{}{}{As students we need to revise our previous documents so that we got valuable documents. }

% BL045
\krav{BL044}{N001}{VPQ-71}{}{}{}{As students we need to plan our thesis document so that it has a sufficient structure.}

% BL046
\krav{BL046}{N/a}{VPQ-72}{}{}{}{As an engineer, I need multiple design options so that I can determine the best design.}

% BL047
\krav{BL047}{N/a}{VPQ-116}{}{}{}{As an engineer I need to tweak the flight controller so that everything works properly.}

% BL048
\krav{BL048}{N/a}{VPQ-126}{AC018}{}{5}{\shortstack[l]{As an engineer, I need to perform tests to gather information so that we can easily present \\ differences between VPQ and FPQ}}